This is the Title

### 2017-03-03 abc/paper/paper.tex
Some notes: I think perhaps JumpInd should pop from the stack.
Delete aforementioned badideas. ASM program needs to record where local frames start. Add x86 encoding to acc. Pipe calls through to individual command translation. Implement Init instruction. Add eicar to paper notes
Separate segment out into its own files. Make fallthrough explicit in tox86. Get into the xblocks layout phase for real. (DOES NOT WORK)

@@

>>>>

Thank you for playing wing commander.

@@

this page confirms the wrap-around with jumps btw:
http://www.felixcloutier.com/x86/Jcc.html
(Probably already in the x86 manual actually?)

Another possibility is to include readable debug information (e.g.
frame layouts) in a separate section.

BTW here is eicar:

X5O!P%@AP[4\PZX54(P^)7CC)7}$EICAR-STANDARD-ANTIVIRUS-TEST-FILE!$H+H*

It does indeed use self-modifying code to create the interrupt
instructions, which it uses to print the string and exit.

histogram of actual bytes used in code segment?
